DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion

### 2014-08-22 paper/paper.tex
Update paper.tex

>>>>

Next we estimate the expected value for each node period.  This is estimated by taking the influence for each newspaper and calculated the weighted sum of newspapers that are producing a given topic in period t.  This weighted sum produces a value for each topic.  The maximum of these values in then chosen for each newspaper and period producing the expected value with the corresponding topic.

Finally, we estimate the total influence of each newspaper by summing the individual influences on each other newspaper.
